Bootstrapping Multi-atlas Hippocampal Segmentation with \mb

### 2013-08-31 paper.Rnw
Montage labels now overlayed, not Plus'ed

\begin{figure}
<<FEP-volumes,cache=FALSE,dependson="setup">>=
SZ_volumes=read.csv("data/SZ_volumes_by_method.csv", sep="\t")
mean_sz_vols = ddply(SZ_volumes, c('Subject', 'Method'), function (df) {
  data.frame(Volume = mean(df$Volume))})

>>>>

\begin{figure}
<<FEP-volumes,cache=TRUE,dependson="setup">>=
SZ_volumes=read.csv("data/SZ_volumes_by_method.csv", sep="\t")
mean_sz_vols = ddply(SZ_volumes, c('Subject', 'Method'), function (df) {
  data.frame(Volume = mean(df$Volume))})
